An Open Platform for Managing Short Programming Exercises

### 2013-06-25 paper/paper.tex
small change explaining motivation

Our primary motivation in developing CloudCoder,
a new programming exercise system,
was {\em freedom}: we wanted a system where
the software and exercises could be freely redistributed, and
were not under the control of any central authority.  This motivation
is not entirely philosophical: we felt that locking down either
the software or the exercises would result in a barrier to adoption,
limiting the potential impact of the system.
As we will discuss in Section~\ref{sec:questions}, we think that there
are some interesting research questions that can be addressed
best through the existence of a ``free like air'' programming
exercise system: for example, we are interested in finding out
whether exercises can be reused effectively in different courses
at different institutions.

>>>>

Our primary motivation in developing CloudCoder,
a new programming exercise system,
was {\em freedom}: we wanted a system where
the software and exercises could be freely redistributed, and
were not under the control of any central authority.  This motivation
is not entirely philosophical: we felt that in any programming
exercise system, locking down either
software or exercises would result in a barrier to adoption,
limiting the potential impact of the system.
As we will discuss in Section~\ref{sec:questions}, we think that there
are some interesting research questions that can be addressed
best through the existence of a ``free like air'' programming
exercise system: for example, we are interested in finding out
whether exercises can be reused effectively in different courses
at different institutions.
